### 2024-06-19 texts/paper_closing.tex
new latex version with new tables

% Created 2024-05-30 do 10:16
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\section*{Identity and the closure of private art museums}

@@

A private museum is entangled in a number of dependencies.
A crucial one is the relationship to the founder, without whom the private museum would not exist.
Founders often control some aspects of management/operations.
While the exact power relationships within museums are hard to observe due to the lack of transparency, which makes it in particular to assess the role of third parties, it is plausible to assume that they cannot exist against the wishes of the founder.
Next to exhibiting the founder's collection, they likely also to a large extent dependent on continued financial contributions of the founder, as museums are chronically unprofitable (which is evidenced by their high share of NPOs or publicly owned/run museums, rather than for-profit companies). 
While the lack of transparency again makes it hard to systematically assess the financial importance of founder contributions to the existence of museums, \textbf{anecdotal} evidence suggests it to be substantial \parencite{Velthuis_Gera_forthcoming_fragility}.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:43 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
   & Founder - alive &  &  & 0.903 & 0.30 & 0 & 1 \\ 
   & Founder - died recently &  &  & 0.019 & 0.13 & 0 & 1 \\ 
   & Founder - died 2+ years ago &  &  & 0.079 & 0.27 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 0.630 & 0.48 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
   & Time Period 2000-2004 &  &  & 0.101 & 0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 0.166 & 0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 0.258 & 0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 0.331 & 0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:51 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_woenv}\\ 
 \hline
  \multicolumn{4}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .02 \; (0.34) & .10 \; (0.34) \\ 
   & Gender - Couple & -.10 \; (0.32) & -.15 \; (0.32) \\ 
   & Founder - died recently & 1.09 \; (0.61) & 1.03 \; (0.61) \\ 
   & Founder - died 2+ years ago & -.06 \; (0.55) & -.19 \; (0.56) \\ 
   \multicolumn{4}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .25 \; (0.42) & .44 \; (0.41) \\ 
   & Self-Identification - Collection & -.46 \; (0.54) & .00 \; (0.50) \\ 
   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.04 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .25 \; (0.35) & .26 \; (0.35) \\ 
   & AN Ranking - Dropped & .51 \; (0.50) & .52 \; (0.49) \\ 
   & Founder name in Museum name & .09 \; (0.28) & .06 \; (0.28) \\ 
   & Exhibition any & -.22 \; (0.27) & -.22 \; (0.27) \\ 
   \multicolumn{4}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .63 \; (0.35) &  \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) &  \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} &  \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  \\ 
   & Great Recession (2008/09) & -1.61 \; (1.01) &  \\ 
   & Covid Pandemic (2020/21) & .39 \; (0.29) &  \\ 
   \hline
 & Museum-years & 6096 & 6096 \\ 
   & Closures & 68 & 68 \\ 
   & log. Likelihood & -338.36 & -351.64 \\ 
   & AIC & 712.73 & 725.28 \\ 
   & BIC & 752.68 & 749.69 \\ 
   \hline 
 \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population}
\end{figure}
\end{document}

>>>>

% Created 2024-06-19 wo 11:22
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\section*{It's so over/Short-lived legacies: The closure of private art museums}

@@

A private museum is entangled in a number of dependencies.
A crucial one is the relationship to the founder, without whom the private museum would not exist.
Founders often control some aspects of management/operations.
While the exact power relationships within museums are hard to observe due to the lack of transparency, which makes it in particular to assess the role of third parties, it is plausible to assume that they cannot exist against the wishes of the founder.
Next to exhibiting the founder's collection, they likely also to a large extent dependent on continued financial contributions of the founder, as museums are chronically unprofitable (which is evidenced by their high share of NPOs or publicly owned/run museums, rather than for-profit companies). 
While the lack of transparency again makes it hard to systematically assess the financial importance of founder contributions to the existence of museums, \textbf{anecdotal} evidence suggests it to be substantial \parencite{Velthuis_Gera_forthcoming_fragility}.
\textcite{Adam_2021_rise}
\begin{itemize}
\item pandemic potentially
\item long-term funding
\item motivations may change
\item difficulties not anticipated
\end{itemize}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May 31 14:28:54 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May 31 14:28:52 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
   & Founder - alive &  &  & 0.903 & 0.30 & 0 & 1 \\ 
   & Founder - died recently &  &  & 0.019 & 0.13 & 0 & 1 \\ 
   & Founder - died 2+ years ago &  &  & 0.079 & 0.27 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 0.630 & 0.48 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
   & Time Period 2000-2004 &  &  & 0.101 & 0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 0.166 & 0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 0.258 & 0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 0.331 & 0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Sat Jun  8 13:10:23 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_wyo} & \multicolumn{1}{l}{r\_pop4\_wtp} & \multicolumn{1}{l}{r\_pop4\_wyotp}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .02 \; (0.34) & .04 \; (0.34) & .03 \; (0.34) & .04 \; (0.34) \\ 
   & Gender - Couple & -.10 \; (0.32) & -.13 \; (0.32) & -.12 \; (0.32) & -.12 \; (0.32) \\ 
   & Founder - died recently & 1.09 \; (0.61) & 1.05 \; (0.62) & 1.09 \; (0.62) & 1.08 \; (0.62) \\ 
   & Founder - died 2+ years ago & -.06 \; (0.55) & -.05 \; (0.55) & -.03 \; (0.55) & -.04 \; (0.55) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .25 \; (0.42) & .22 \; (0.42) & .22 \; (0.42) & .22 \; (0.42) \\ 
   & Self-Identification - Collection & -.46 \; (0.54) & -.52 \; (0.54) & -.53 \; (0.54) & -.53 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.12 \; (0.31)^{***} & 1.12 \; (0.31)^{***} & 1.12 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .25 \; (0.35) & .29 \; (0.36) & .30 \; (0.36) & .30 \; (0.36) \\ 
   & AN Ranking - Dropped & .51 \; (0.50) & .39 \; (0.50) & .41 \; (0.50) & .40 \; (0.50) \\ 
   & Founder name in Museum name & .09 \; (0.28) & .12 \; (0.28) & .11 \; (0.28) & .11 \; (0.28) \\ 
   & Exhibition any & -.22 \; (0.27) & -.20 \; (0.27) & -.20 \; (0.27) & -.20 \; (0.27) \\ 
   & Opening year &  & .12 \; (0.04)^{**} &  & .03 \; (0.10) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & Time Period 2005-2009 &  &  & .46 \; (1.16) & .30 \; (1.25) \\ 
   & Time Period 2010-2014 &  &  & 1.55 \; (1.04) & 1.22 \; (1.42) \\ 
   & Time Period 2015-2019 &  &  & 2.12 \; (1.02)^{*} & 1.63 \; (1.77) \\ 
   & Time Period 2020-2024 &  &  & 2.14 \; (1.04)^{*} & 1.54 \; (2.06) \\ 
   & PM density (country) & .63 \; (0.35) & .58 \; (0.40) & .59 \; (0.40) & .59 \; (0.40) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .26 \; (0.09)^{**} & .26 \; (0.09)^{**} & .26 \; (0.09)^{**} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .23 \; (0.08)^{**} & .23 \; (0.08)^{**} & .23 \; (0.08)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.08 \; (0.03)^{**} & -.08 \; (0.03)^{**} & -.08 \; (0.03)^{**} \\ 
   & Great Recession (2008/09) & -1.61 \; (1.01) & -1.00 \; (1.04) &  &  \\ 
   & Covid Pandemic (2020/21) & .39 \; (0.29) & -.36 \; (0.35) &  &  \\ 
   \hline
 & Museums & 503 & 503 & 503 & 503 \\ 
   & Museum-years & 6096 & 6096 & 6096 & 6096 \\ 
   & Closures & 68 & 68 & 68 & 68 \\ 
   & log. Likelihood & -338.36 & -332.02 & -331.91 & -331.85 \\ 
   & AIC & 712.73 & 702.04 & 703.82 & 705.70 \\ 
   & BIC & 752.68 & 744.21 & 748.21 & 752.31 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population}
\end{figure}

covid effect may take longer to be effective
\end{document}
